---
title: "Lab5"
author: "J Bai"
date: "10/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Activities
### 1. Matrix and vector multiplication: write a function that will multiply a matrix and a vector (without built-in matrix multiplication function). A%*%B is not allowed.
```{r}
mat_vec_mult <- function(mat, vec) {

  n <- nrow(mat)
  number_of_column <- ncol(mat)
  if(number_of_column != length(vec)) {
    stop("non-conformable arguments")
  }
  result <- matrix(nrow = n, ncol = 1)
  for(i in 1:n) {
    result[i,1] <- sum(mat[i,] * vec)
  }
  return(result)
  
}
A = matrix(1:12, nrow = 4)
b <- c(1,2,3)

mat_vec_mult(A, b)

# teacher's answer
teacher_version_mat_vec_mult <- function(A, x) {
  m <- nrow(A)
  n <- ncol(A)
  y <- matrix(0, nrow = m)
  for(j in 1:n) {
    for(i in 1:m) {
      y[i] = y[i] + A[i,j]*x[j]
    }
  }
  return(y)
}
teacher_version_mat_vec_mult(A, b)
```


### 2.Suppose you are betting that you get at least one six in 4 throws of a die. Write a function that simulates one round of the game and prints out whether you win or lose.
```{r}
betting <- function(guess, throws) {
  # for one round, at least one "guess"" appears in "throws" throws of a die.
  for(i in 1:throws) {
    result <- rolling()
    if(guess == result) {
      #print("You Win")
      return(1)
    }
  }
  #print("You Lose")
  return(0)
  
}

rolling <- function() {
  sample(1:6, 1, replace = T)
}

betting(6, 4)


```

## Assignment
### 1. Modify your function from the Problem 2 (Lab5 Activity). The function should simulate N rounds of the game (instead of just one) and return the proportion of times you win the bet. Run the function with N = 1000 and 10000.
```{r}
bettingN <- function(guess, throws, N) {
  # play the game for N rounds
  # for each round, at least one "guess"" appears in "throws" throws of a die.
  countWin <- 0
  for(i in 1:N) {
    countWin = countWin + betting(guess, throws)
  }
  return(countWin/N)
}

bettingN(6, 4, 1000) 
bettingN(6, 4, 10000) 
```

### 2. Write a function that will find the smallest element of a given vector (built-in min() is not allowed). Your function should return the smallest element and index of the smallest element. 
Ex. vector is (1, 4, 2, 0, 5), then the smallest element - 0 and index is 4.
```{r}
minElementAndIndex <- function(v) {
  small <- v[1]
  for(i in 1:length(v)) {
    if(v[i] < small) {
      small = v[i]
      result <- c(small, i)
    }
  }
  print(paste("the smallest element is ", result[1], " and index is ", result[2]))
  return(result)
}

minElementAndIndex(c(1,4,2,0,5))
```


